### 2016-10-28 capability-machine.tex
Spell checking

\documentclass{article}

@@

\begin{document}
\begin{flushright}
\today
\end{flushright}
\section{Domains and Notation}
\begin{align*}
\Addrs &::= \nats & & &
\Words &::= \Caps + \ints \\
\Regs  &::= \RegName \rightarrow \Words & & &
\Heaps &::= \Addrs \rightarrow \Words \\
\Perms &::= \{ \noperm, \readonly, \readwrite, \readwritel, \exec, \entry, \rwx, \rwlx\} & & &
\Mems  &::= \Regs \times \Heaps \\
\Caps  &::= (\Perms \times \Globals) \times \Addrs \times \Addrs \times \Addrs & & &
\Confs &::= \Mems + \{\failed, \halted \times \Mems\} \\
\HeapSegments &::= \Addrs \parfun \Words & & &
\Globals & ::= \{\glob, \local \}
\end{align*}
Local capabilities have been added by adding a new domain $\Globals$ which represents whether a capabaility is local or global. Two new permissions $\readwritel$ and $\rwlx$ that permits writing local capabilities. They are otherwise the same as their non-''permit write local'' counterparts.

@@

Things to note:
\begin{itemize}
\item $\RegName$ contains $\pcreg$, but is otherwise a sufficiently
  large finite set.
\item Table~\ref{tab:permission-list} describes what all the permissions grant acces to.
\item Figure~\ref{fig:perm-hier} shows the ordering of the permissions, i.e, the elements of $\Perms$.
\item Figure~\ref{fig:glob-hier} shows the ordering of $\local$ and $\glob$, i.e., the elements of $\Globals$.
\item The ordering of $\Perms \times \Globals$ is pointwise.
\end{itemize}

@@

\lau{Dominique, apparently there was a reason I had not added the new condition in store to $\writeAllowed{}$. The new condition depends on a case distinction on $w$. It is only if $w$ is a capabilty that we look into whether it is local or not. But even if $w$ is just an integer, we still need the capability we write through to have some kind of write permission.}

After adding local capabilities, most of the definitions have changed slightly to take into the account new form the capabilties take. The only two instructions that have undergone enough change to deserve to be mentioned are $\store{}$ and $\restrict{}{}{}$.

@@

\subsection{Ticket Dispenser}
\label{sec:tick-disp}
\newcommand{\hsfoot}{\hs_\var{footprint}}
\newcommand{\hsframe}{\hs_\var{frame}}
\newcommand{\size}{\var{size}}
\newcommand{\rio}{r_{io}}
\newcommand{\adv}{\codelabel{adv}}
\newcommand{\advb}{\var{adv_{base}}}
\newcommand{\adve}{\var{adv_{end}}}
\newcommand{\initb}{\var{init}_{base}}
\newcommand{\inite}{\var{init}_{end}}
\newcommand{\mrlen}{5cm}
\newcommand{\retm}{\var{ret}_{\malloc}}
\newcommand{\reta}{\var{ret}_{\adv}}
\newcommand{\base}{\var{base}}
\newcommand{\eend}{\var{end}}
\newcommand{\bracket}[1]{\multirow{#1}{*}{\ensuremath{
 \left . \vphantom{\begin{array}{l}
 \ifthenelse{\equal{#1}{1}}{3\\}{
    \ifthenelse{\equal{#1}{2}}{3\\3\\}{
    \ifthenelse{\equal{#1}{3}}{3\\3\\3\\}{
    \ifthenelse{\equal{#1}{4}}{3\\3\\3\\3\\}{
    \ifthenelse{\equal{#1}{5}}{3\\3\\3\\3\\3\\}{
    \ifthenelse{\equal{#1}{6}}{3\\3\\3\\3\\3\\3\\}{
      3\\3\\3\\3\\3\\3\\3\\ %7
  }}}}}}
  \end{array}} \right \}}}
}
\newcommand{\annotate}[2]{\multirow{#1}{\mrlen}{\scriptsize #2}}
\lau{Has not been adjusted since local capabilties were added.}

@@

\initb:     & \store{\refheap{\rio}}{-1} & \bracket{1} & \annotate{1}{Initialize io to $-1$} \\

@@

\section{Logical Relation'}
\subsection{Worlds}
Define the domain $\Views$ as follows
\[
  \Views = \{\perma,\temp,\revoked\}
\]
Using the ordering where $\revoked \future \temp$ and $\future$ is otherwise reflexive, and a family of equivalences where everything is equal at 0 and othervise the equivalences are ``normal'' equality. We claim this is a preordered \cofe{}. %TODO prove this claim! And show the new "region" is a preordered cofe with the claimed ordering.

@@

Rewoking all temporary regions:

@@

This cannot be solved with sets, so we use preordered complete ordered families of equivalences where it is possible to solve such an equation that ressembles the above one, namely it is possible to find an isomorphism $\xi$ and preordered \cofe{} $W$ such that
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]

\begin{definition}[o.f.e's]
  An ordered family of equivalences (o.f.e.) is a set and a family of equivalences, $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$. The familly of equivalences have to satisfy the following properties
  \begin{itemize}
  \item $\nequal[0]$ is a total relation on $X$
  \item $\forall n \ldotp \forall x,y \in S \ldotp x \nequal[n+1] y \Rightarrow x \nequal y$
  \item $\forall x,y \ldotp(\forall n \ldotp x \nequal y) \Rightarrow x=y$
  \end{itemize}
\end{definition}

\dominique{I suppose you're using a standard ultrametric metric to make an
  o.f.e. a metric space?}
\begin{definition}[\cofes]
  A complete orderede family of equivalences is an o.f.e.\ $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$ where all Cauchy sequences in $X$ have a limit in $X$.
\end{definition}

\begin{definition}[Preordered \cofes]
  A preordered \cofe{}\ is a \cofe{}\ equiped with a preorder on $X$, $\left(X, \left(\nequal\right)_{n=0}^{\infty}, \future \right)$. 
  \begin{itemize}
  \item The ordering preserves limits. That is, for Cauchy chains $\{a_n\}_n$ and $\{b_n\}_n$ in $X$ if $\{a_n\}_n \future\{b_n\}_n$, then $\lim \{a_n\}_n \future \lim \{b_n\}_n$.
  \end{itemize}
  % Preorder:
  % \begin{itemize}
  % \item $\forall x \in X \ldotp x \future x$
  % \item $\forall x,y,z \in X \ldotp x \future y \land y \future z \Rightarrow x \future z$
  % \end{itemize}
\end{definition}

@@

The category of \cofes{} is the category whith \cofes{} as objects and non-expansive functions as morphisms. We denote this category $\CatC$. The category of preordered \cofes{} has preordered \cofes{} as objects and monotone and non-expansive functions as morphisms. We denote this category $\CatP$.

@@

\begin{lemma}[$F$ locally non-expansive]
\label{lem:F-loc-ne}
For all $f, g : X \fun Y$, if $f \nequal g$, then $F(f) \nequal F(g)$.
\end{lemma}
With $F$ being locally-non-expansive, we can pre- or post-compose with later ($\blater$) to get a locally contractive function. In this case we construct $F'$ by post-copmosition of $\blater$:
\[
  F'(\Wor) = \blater (F(\Wor))
\]
We have a theorem that gives us a solution to the recurisve domain equation
\[
  \Wor \cong F'(\Wor) = \blater (\nats \finparfun (\States \times \Rel \times (\States \fun \Wor \monnefun \UPred{\HeapSegments} )))
\]
The solution to the recursice domain equations is presented by \cite{Birkedal:2010:TCS:411:4102-4122}. They solve it in pre-ordered, non-empty, complete, 1-bounded ultrametric spaces, but they have a simple correspondence to pre-ordered \cofes{}.

@@

\subsection{Logical Relation Setup}
\label{subsec:logical-relation-setup}
Our logical relation is defined using multiple recursive definitions, so the definitions in the following subsections are defined simultaneously. We want to define the value relation as the fixed-point given by Banach's fixed-point theorem, so all our definitions will be parameterized with the value relation.
\subsubsection{Observation Relation}
\label{subsubsec:observation-relation}
In order to define the expression relation, we define an observation relation.
\begin{align*}
  \observations \quad : & \quad  \Worlds \nefun \UPred{\Regs \times \HeapSegments} \\
  \observations (W) \defeq & \{ \npair{(\reg,\hs)} \mid \\
                           & \quad (\forall \heap_f, \heap', i \leq n \ldotp (\reg,\hs \uplus \heap_f) \step[i] (\halted,\heap')  \\
                           & \qquad \Rightarrow \exists W' \future W \ldotp\exists \hs' \ldotp \heap' = \hs' \uplus \heap_f \land \heapSat[\hs']{n-i}{W'}
\end{align*}
A pair of a register and a heap segment is ``good'' if we can put it together with a frame heap, so we can execute it. The execution should then end up in a heap where the frame remains the same and the remaining heap segment satisfies the world.

@@

\subsubsection{Regiser-File Relation}
\label{subsubsec:register-file-relation}
This relation is used in the definition of the continuation relation as well as the expression relation.
\begin{align*}
  \stdrr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Regs} \\
  \stdrr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp
                     \begin{aligned}[t]
                       \{ \npair{\reg} \mid & \;\forall r \in \RegName \setminus \{\pcreg\} \ldotp \\
                                            & \;\quad  \npair{\reg(r)} \in \stdvr(W) \}
                     \end{aligned}
\end{align*}
Well-formedness lemmas for this definition:
\begin{lemma}[Register relation uniformity]
\label{lem:reg-dc}
  \begin{align*}
    &\forall \stdvr, n' \leq n \ldotp \forall W \ldotp \forall \reg \ldotp\\
    &\quad \npair{\reg} \in \stdrr(\stdvr)(W) \Rightarrow \npair[n']{\reg} \in \stdrr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

\subsubsection{Capability Conditions}
\label{subsubsec:capability-conditions}
The definition of the value relation has the same conditions several times, so to define it consisely, we define the following conditions.
\begin{align*}
  & \readCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \readCond{}(\stdvr)(\start,\addrend,W) =        
  \begin{aligned}[t]
    \{ n \mid & \;\exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota_{\start',\addrend'}(\stdvr) \}
  \end{aligned}\\
 & \\
  & \writeCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \writeCond{}(\stdvr)(\start,\addrend, W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \; \qquad W(r) \nequal[n-1] \iota_{\start',\addrend'}(\stdvr)  \}
  \end{aligned}\\
 & \\
  & \execCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Perms \times \Worlds) \monnefun \DCPred{\nats} \\
  & \execCond{}(\stdvr)(\start,\addrend,\perm,W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
              & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned} \\
 & \\
  & \entryCond{} : \;  (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^3 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \entryCond{}(\stdvr)(\start,\addrend,\addr,W) =
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned}
\end{align*}

@@

\subsection{Logical Relation Definitions}
\label{subsec:logical-relation-definitions}
\lau{This section introduces the definitions, we started working with, so it is here so we don't have to rewrite everything.}
Here we state the definitions, we will use for pratical purposes.  Assume $V$ is the fixed point given by Banach's fixed point theorem as described in Section~\ref{subsubsec:value-relation}. In general the definitions here will be the same as in Section~\ref{subsec:logical-relation-setup}, but but applied to $V$ when applicable. As they are essentially the same, we will reuse the names.

@@

For natural number $n$, adresses $\start$, $\addrend$, and $\addr$, permission $\perm$, and world $W$, we define the capability conditions as follows
\begin{align*}
  \readCond{n,W,\start,\addrend}        & \text{ iff } n \in \readCond{}(V)(\start,\addrend,W)\\
  \writeCond{n,W,\start,\addrend}       & \text{ iff } n \in \writeCond{}(V)(\start,\addrend,W)\\
  \execCond{n,W,\start,\addrend,\perm}  & \text{ iff } n \in \execCond{}(V)(\start,\addrend,p,W)\\
  \entryCond{n,W,\start,\addrend,\addr} & \text{ iff } n \in \entryCond{}(V)(\start,\addrend,\addr,W)
\end{align*}
The well-formedness lemmas of course still hold for this new presentation.

\subsection{Further Standard Regions}
\label{subsec:further-standard-regions}
We have already defined the standard region $\iota_{\start,\addrend}$ which ensures that all the words in the region are in the value relation. See Section~\ref{subsubsec:standard-region}. We here define another usefull region, namely the one that requires all the words in the region to be the constant 0.
\[
  \iota_{\start,\addrend}^0 \; : \; \Regions
\]
\begin{align*}
  \iota_{\start,\addrend}^0 & \defeq ((\start,\addrend),=,H_{\var{std}}^0) \\
  H_{\var{std}}^0\; (\start,\addrend)\; W     & \defeq\left\{ \npair{\heapseg} \middle| 
                                                     \begin{aligned}
                                                       & \dom(\heapseg) = [\start,\addrend] \land \\
                                                       & \forall \addr \in \dom(\heapseg) \ldotp \heapseg(\addr) = 0  
                                                     \end{aligned} \right\}
\end{align*}

\begin{lemma}[$\iota_{\start,\addrend}^0$ is well-defined]\label{lem:std-z-region-wd}\forcenewline
\begin{itemize}
  \item $H_{\var{std}}^0$ is non-expansive.
  \item For all adresses $\start$
    and $\addrend$, $ H_{\var{std}}^0 \; (\start,\addrend)$ is monotone and non-expansive.
  \item  $=$ is a reflexive and transitive relation.
\end{itemize}
\end{lemma}

@@

\case{\jmp{r}}
Here the first execution step is:
\[
  \Phi \step (\reg[r_0 \mapsto c, \pcreg \mapsto \updatePcPerm{\reg'(r)}],h)
\]
We now consider four cases 
\begin{description}
\item[Case $\reg'(r) = (\rwx,b',e',a')$:] In this case, we want to appeal to the induction hypothesis. To do so, we need to argue that we have $\writeCond{n'-1,b',e',a'}$. If $r=\pcreg$, then we have this by assumption \ref{eq:ftlr:rwx-assump} and uniformity. If $r \neq \pcreg$, then if $r= r_0$, then by assumption \ref{eq:ftlr:cont-in-stdkr}, we have $\npair[n']{c} \in \stdkr(W)$ which entails $\npair[n']{c} \in \stdvr(W)$ which together with uniformity gives the $\writeCond{}$ due to the permission. Otherwise, the same folloes from assumption \ref{eq:ftlr:reg-in-stdrr} and uniformity.

@@

where advfunction1() and advfunction2() are adversary functions. In the standard
C treatment of the stack, advfunction2() would get the same stack pointer as
advfunction1(). This is supposed to be safe since advfunction1() cannot have
kept capabilities for the stack after its execution. But what if we require that
the two functions have no way of communicating with each other? Concretely,
advfunction1() has access to some secrets that must not be leaked to
advfunction2(). How can we prevent advfunction1() from storing the secret
somewhere on the stack and relying on advfunction2() from receiving the same
stack pointer where it can read the secret? The most obvious solution seems to
be that we should fully clear the stack (overwrite it with zeros) after the
return of any adversary function, but this could cause an important overhead.
Perhaps the processor should accomodate this with a special instruction that can
zero the entire array that a capability points to?

@@

\begin{definition}[Set \cofe{}\ Construction]
  Given a set $X$, then $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$ is a \cofe{}\ where all the equivalences are equiality.
\end{definition}

@@

  Idenntity distributes over $R$, $R(\id) = \id$.
  \[
    R(id) = \lambda (s,\Phi,H) \ldotp  (s,\Phi,\id(H)) = \lambda (s,\Phi,H) \ldotp  (s,\Phi,H) = \id
  \]
\end{proof}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}

@@

\begin{document}
\begin{flushright}
\today
\end{flushright}
\section{Domains and Notation}
\begin{align*}
\Addrs &::= \nats & & &
\Words &::= \Caps + \ints \\
\Regs  &::= \RegName \rightarrow \Words & & &
\Heaps &::= \Addrs \rightarrow \Words \\
\Perms &::= \{ \noperm, \readonly, \readwrite, \readwritel, \exec, \entry, \rwx, \rwlx\} & & &
\Mems  &::= \Regs \times \Heaps \\
\Caps  &::= (\Perms \times \Globals) \times \Addrs \times \Addrs \times \Addrs & & &
\Confs &::= \Mems + \{\failed, \halted \times \Mems\} \\
\HeapSegments &::= \Addrs \parfun \Words & & &
\Globals & ::= \{\glob, \local \}
\end{align*}
Local capabilities have been added by adding a new domain $\Globals$ which represents whether a capability is local or global. Two new permissions $\readwritel$ and $\rwlx$ that permits writing local capabilities. They are otherwise the same as their non-''permit write local'' counterparts.

@@

Things to note:
\begin{itemize}
\item $\RegName$ contains $\pcreg$, but is otherwise a sufficiently
  large finite set.
\item Table~\ref{tab:permission-list} describes what all the permissions grant access to.
\item Figure~\ref{fig:perm-hier} shows the ordering of the permissions, i.e, the elements of $\Perms$.
\item Figure~\ref{fig:glob-hier} shows the ordering of $\local$ and $\glob$, i.e., the elements of $\Globals$.
\item The ordering of $\Perms \times \Globals$ is point wise.
\end{itemize}

@@

\lau{Dominique, apparently there was a reason I had not added the new condition in store to $\writeAllowed{}$. The new condition depends on a case distinction on $w$. It is only if $w$ is a capability that we look into whether it is local or not. But even if $w$ is just an integer, we still need the capability we write through to have some kind of write permission.}

After adding local capabilities, most of the definitions have changed slightly to take into the account new form the capabilities take. The only two instructions that have undergone enough change to deserve to be mentioned are $\store{}$ and $\restrict{}{}{}$.

@@

\subsection{Ticket Dispenser}
\label{sec:tick-disp}
\newcommand{\hsfoot}{\hs_\var{footprint}}
\newcommand{\hsframe}{\hs_\var{frame}}
\newcommand{\size}{\var{size}}
\newcommand{\rio}{r_{io}}
\newcommand{\adv}{\codelabel{adv}}
\newcommand{\advb}{\var{adv_{base}}}
\newcommand{\adve}{\var{adv_{end}}}
\newcommand{\initb}{\var{init}_{base}}
\newcommand{\inite}{\var{init}_{end}}
\newcommand{\mrlen}{5cm}
\newcommand{\retm}{\var{ret}_{\malloc}}
\newcommand{\reta}{\var{ret}_{\adv}}
\newcommand{\base}{\var{base}}
\newcommand{\eend}{\var{end}}
\newcommand{\bracket}[1]{\multirow{#1}{*}{\ensuremath{
 \left . \vphantom{\begin{array}{l}
 \ifthenelse{\equal{#1}{1}}{3\\}{
    \ifthenelse{\equal{#1}{2}}{3\\3\\}{
    \ifthenelse{\equal{#1}{3}}{3\\3\\3\\}{
    \ifthenelse{\equal{#1}{4}}{3\\3\\3\\3\\}{
    \ifthenelse{\equal{#1}{5}}{3\\3\\3\\3\\3\\}{
    \ifthenelse{\equal{#1}{6}}{3\\3\\3\\3\\3\\3\\}{
      3\\3\\3\\3\\3\\3\\3\\ %7
  }}}}}}
  \end{array}} \right \}}}
}
\newcommand{\annotate}[2]{\multirow{#1}{\mrlen}{\scriptsize #2}}
\lau{Has not been adjusted since local capabilities were added.}

@@

\initb:     & \store{\refheap{\rio}}{-1} & \bracket{1} & \annotate{1}{Initialise io to $-1$} \\

@@

\section{Logical Relation'}
\subsection{Worlds}
Define the domain $\Views$ as follows
\[
  \Views = \{\perma,\temp,\revoked\}
\]
Using the ordering where $\revoked \future \temp$ and $\future$ is otherwise reflexive, and a family of equivalences where everything is equal at 0 and otherwise the equivalences are ``normal'' equality. We claim this is a preordered \cofe{}. %TODO prove this claim! And show the new "region" is a preordered cofe with the claimed ordering.

@@

Revoking all temporary regions:

@@

This cannot be solved with sets, so we use preordered complete ordered families of equivalences where it is possible to solve such an equation that resembles the above one, namely it is possible to find an isomorphism $\xi$ and preordered \cofe{} $W$ such that
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]

\begin{definition}[o.f.e's]
  An ordered family of equivalences (o.f.e.) is a set and a family of equivalences, $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$. The family of equivalences have to satisfy the following properties
  \begin{itemize}
  \item $\nequal[0]$ is a total relation on $X$
  \item $\forall n \ldotp \forall x,y \in S \ldotp x \nequal[n+1] y \Rightarrow x \nequal y$
  \item $\forall x,y \ldotp(\forall n \ldotp x \nequal y) \Rightarrow x=y$
  \end{itemize}
\end{definition}

\dominique{I suppose you're using a standard ultrametric metric to make an
  o.f.e. a metric space?}
\begin{definition}[\cofes]
  A complete ordered family of equivalences is an o.f.e.\ $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$ where all Cauchy sequences in $X$ have a limit in $X$.
\end{definition}

\begin{definition}[Preordered \cofes]
  A preordered \cofe{}\ is a \cofe{}\ equipped with a preorder on $X$, $\left(X, \left(\nequal\right)_{n=0}^{\infty}, \future \right)$. 
  \begin{itemize}
  \item The ordering preserves limits. That is, for Cauchy chains $\{a_n\}_n$ and $\{b_n\}_n$ in $X$ if $\{a_n\}_n \future\{b_n\}_n$, then $\lim \{a_n\}_n \future \lim \{b_n\}_n$.
  \end{itemize}
  % Preorder:
  % \begin{itemize}
  % \item $\forall x \in X \ldotp x \future x$
  % \item $\forall x,y,z \in X \ldotp x \future y \land y \future z \Rightarrow x \future z$
  % \end{itemize}
\end{definition}

@@

The category of \cofes{} is the category with \cofes{} as objects and non-expansive functions as morphisms. We denote this category $\CatC$. The category of preordered \cofes{} has preordered \cofes{} as objects and monotone and non-expansive functions as morphisms. We denote this category $\CatP$.

@@

\begin{lemma}[$F$ locally non-expansive]
\label{lem:F-loc-ne}
For all $f, g : X \fun Y$, if $f \nequal g$, then $F(f) \nequal F(g)$.
\end{lemma}
With $F$ being locally-non-expansive, we can pre- or post-compose with later ($\blater$) to get a locally contractive function. In this case we construct $F'$ by post-composition of $\blater$:
\[
  F'(\Wor) = \blater (F(\Wor))
\]
We have a theorem that gives us a solution to the recursive domain equation
\[
  \Wor \cong F'(\Wor) = \blater (\nats \finparfun (\States \times \Rel \times (\States \fun \Wor \monnefun \UPred{\HeapSegments} )))
\]
The solution to the recursive domain equations is presented by \cite{Birkedal:2010:TCS:411:4102-4122}. They solve it in pre-ordered, non-empty, complete, 1-bounded ultrametric spaces, but they have a simple correspondence to pre-ordered \cofes{}.

@@

\subsection{Logical Relation Setup}
\label{subsec:logical-relation-setup}
Our logical relation is defined using multiple recursive definitions, so the definitions in the following subsections are defined simultaneously. We want to define the value relation as the fixed-point given by Banach's fixed-point theorem, so all our definitions will be parameterised with the value relation.
\subsubsection{Observation Relation}
\label{subsubsec:observation-relation}
In order to define the expression relation, we define an observation relation.
\begin{align*}
  \observations \quad : & \quad  \Worlds \nefun \UPred{\Regs \times \HeapSegments} \\
  \observations (W) \defeq & \{ \npair{(\reg,\hs)} \mid \\
                           & \quad (\forall \heap_f, \heap', i \leq n \ldotp (\reg,\hs \uplus \heap_f) \step[i] (\halted,\heap')  \\
                           & \qquad \Rightarrow \exists W' \future W \ldotp\exists \hs' \ldotp \heap' = \hs' \uplus \heap_f \land \heapSat[\hs']{n-i}{W'}
\end{align*}
A pair of a register and a heap segment is ``good'' if we can put it together with a frame heap, so we can execute it. The execution should then end up in a heap where the frame remains the same and the remaining heap segment satisfies the world.

@@

\subsubsection{Register-File Relation}
\label{subsubsec:register-file-relation}
This relation is used in the definition of the continuation relation as well as the expression relation.
\begin{align*}
  \stdrr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Regs} \\
  \stdrr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp
                     \begin{aligned}[t]
                       \{ \npair{\reg} \mid & \;\forall r \in \RegName \setminus \{\pcreg\} \ldotp \\
                                            & \;\quad  \npair{\reg(r)} \in \stdvr(W) \}
                     \end{aligned}
\end{align*}
Well-formedness lemmas for this definition:
\begin{lemma}[Register relation uniformity]
\label{lem:reg-dc}
  \begin{align*}
    &\forall \stdvr, n' \leq n \ldotp \forall W \ldotp \forall \reg \ldotp\\
    &\quad \npair{\reg} \in \stdrr(\stdvr)(W) \Rightarrow \npair[n']{\reg} \in \stdrr(\stdvr)(W)
  \end{align*}
\end{lemma}

@@

\subsubsection{Capability Conditions}
\label{subsubsec:capability-conditions}
The definition of the value relation has the same conditions several times, so to define it concisely, we define the following conditions.
\begin{align*}
  & \readCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \readCond{}(\stdvr)(\start,\addrend,W) =        
  \begin{aligned}[t]
    \{ n \mid & \;\exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubeq[n-1] \iota_{\start',\addrend'}(\stdvr) \}
  \end{aligned}\\
 & \\
  & \writeCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \writeCond{}(\stdvr)(\start,\addrend, W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \exists r \in \RegionNames \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \; \qquad W(r) \nequal[n-1] \iota_{\start',\addrend'}(\stdvr)  \}
  \end{aligned}\\
 & \\
  & \execCond{} : \; (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^2 \times \Perms \times \Worlds) \monnefun \DCPred{\nats} \\
  & \execCond{}(\stdvr)(\start,\addrend,\perm,W) = 
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \forall \addr \in [\start,\addrend] \ldotp \\
              & \; \qquad \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned} \\
 & \\
  & \entryCond{} : \;  (\Worlds \monnefun \UPred{\Words}) \nefun (\Addrs^3 \times \Worlds) \monnefun \DCPred{\nats} \\
  & \entryCond{}(\stdvr)(\start,\addrend,\addr,W) =
  \begin{aligned}[t]
    \{ n \mid & \; \forall n' < n \ldotp \forall W' \future W \ldotp \\
              & \; \quad \npair[n']{(\exec,\start,\addrend,\addr)} \in \stder(\stdvr)(W') \}
  \end{aligned}
\end{align*}

@@

\subsection{Logical Relation Definitions}
\label{subsec:logical-relation-definitions}
\lau{This section introduces the definitions, we started working with, so it is here so we don't have to rewrite everything.}
Here we state the definitions, we will use for practical purposes.  Assume $V$ is the fixed point given by Banach's fixed point theorem as described in Section~\ref{subsubsec:value-relation}. In general the definitions here will be the same as in Section~\ref{subsec:logical-relation-setup}, but but applied to $V$ when applicable. As they are essentially the same, we will reuse the names.

@@

For natural number $n$, addresses $\start$, $\addrend$, and $\addr$, permission $\perm$, and world $W$, we define the capability conditions as follows
\begin{align*}
  \readCond{n,W,\start,\addrend}        & \text{ iff } n \in \readCond{}(V)(\start,\addrend,W)\\
  \writeCond{n,W,\start,\addrend}       & \text{ iff } n \in \writeCond{}(V)(\start,\addrend,W)\\
  \execCond{n,W,\start,\addrend,\perm}  & \text{ iff } n \in \execCond{}(V)(\start,\addrend,p,W)\\
  \entryCond{n,W,\start,\addrend,\addr} & \text{ iff } n \in \entryCond{}(V)(\start,\addrend,\addr,W)
\end{align*}
The well-formedness lemmas of course still hold for this new presentation.

\subsection{Further Standard Regions}
\label{subsec:further-standard-regions}
We have already defined the standard region $\iota_{\start,\addrend}$ which ensures that all the words in the region are in the value relation. See Section~\ref{subsubsec:standard-region}. We here define another useful region, namely the one that requires all the words in the region to be the constant 0.
\[
  \iota_{\start,\addrend}^0 \; : \; \Regions
\]
\begin{align*}
  \iota_{\start,\addrend}^0 & \defeq ((\start,\addrend),=,H_{\var{std}}^0) \\
  H_{\var{std}}^0\; (\start,\addrend)\; W     & \defeq\left\{ \npair{\heapseg} \middle| 
                                                     \begin{aligned}
                                                       & \dom(\heapseg) = [\start,\addrend] \land \\
                                                       & \forall \addr \in \dom(\heapseg) \ldotp \heapseg(\addr) = 0  
                                                     \end{aligned} \right\}
\end{align*}

\begin{lemma}[$\iota_{\start,\addrend}^0$ is well-defined]\label{lem:std-z-region-wd}\forcenewline
\begin{itemize}
  \item $H_{\var{std}}^0$ is non-expansive.
  \item For all addresses $\start$
    and $\addrend$, $ H_{\var{std}}^0 \; (\start,\addrend)$ is monotone and non-expansive.
  \item  $=$ is a reflexive and transitive relation.
\end{itemize}
\end{lemma}

@@

\case{\jmp{r}}
Here the first execution step is:
\[
  \Phi \step (\reg[r_0 \mapsto c, \pcreg \mapsto \updatePcPerm{\reg'(r)}],h)
\]
We now consider four cases 
\begin{description}
\item[Case $\reg'(r) = (\rwx,b',e',a')$:] In this case, we want to appeal to the induction hypothesis. To do so, we need to argue that we have $\writeCond{n'-1,b',e',a'}$. If $r=\pcreg$, then we have this by assumption \ref{eq:ftlr:rwx-assump} and uniformity. If $r \neq \pcreg$, then if $r= r_0$, then by assumption \ref{eq:ftlr:cont-in-stdkr}, we have $\npair[n']{c} \in \stdkr(W)$ which entails $\npair[n']{c} \in \stdvr(W)$ which together with uniformity gives the $\writeCond{}$ due to the permission. Otherwise, the same follows from assumption \ref{eq:ftlr:reg-in-stdrr} and uniformity.

@@

where advfunction1() and advfunction2() are adversary functions. In the standard
C treatment of the stack, advfunction2() would get the same stack pointer as
advfunction1(). This is supposed to be safe since advfunction1() cannot have
kept capabilities for the stack after its execution. But what if we require that
the two functions have no way of communicating with each other? Concretely,
advfunction1() has access to some secrets that must not be leaked to
advfunction2(). How can we prevent advfunction1() from storing the secret
somewhere on the stack and relying on advfunction2() from receiving the same
stack pointer where it can read the secret? The most obvious solution seems to
be that we should fully clear the stack (overwrite it with zeros) after the
return of any adversary function, but this could cause an important overhead.
Perhaps the processor should accommodate this with a special instruction that can
zero the entire array that a capability points to?

@@

\begin{definition}[Set \cofe{}\ Construction]
  Given a set $X$, then $\left(X, \left(\nequal\right)_{n=0}^{\infty} \right)$ is a \cofe{}\ where all the equivalences are equality.
\end{definition}

@@

  Identity distributes over $R$, $R(\id) = \id$.
  \[
    R(id) = \lambda (s,\Phi,H) \ldotp  (s,\Phi,\id(H)) = \lambda (s,\Phi,H) \ldotp  (s,\Phi,H) = \id
  \]
\end{proof}
